Intervention Bandits

### 2015-01-16 causal-bandit/c-bandit.tex
gets regret bound for observe stage for simplest possible model
working on regret consdiering overlap of more than one arm

If \ref{eq:overlap3} is true, we can bound the probability of overlap at some timestep $t$ with the union bound of the probability that either \ref{eq:overlap1} or \ref{eq:overlap2} are false.

\eqn {
P(overlap) = P(n \geq t) \leq 
P(\mu^* - \hat{\mu}^* \geq \epsilon) + P(\hat{\mu}_i - \mu_i \geq \epsilon)  \;\;\;\text{ if } \epsilon \leq a/4
}

Let $\epsilon = a/4$

\eqn {
P(n > t) \leq & e^{-nD(p_{ij}+p (a/4) || p_{ij})} +e^{-nD(p_{ij}-p (a/4) || p_{ij})} \\
\leq & \;\;\;?
}

Where $p_ij = P(Y = 1, X_i = j) \leq P(X_i=j) = p \;\;\; \forall(i,j)$

Now

\eqn {
E[n] = \sum_{t=1}^\infty P(n \geq t)
}

>>>>

If \ref{eq:overlap3} is true, we can bound the probability of overlap  been the confidence intervals of the best arm and one of the other arms, $k$, at some timestep $t$ with the union bound of the probability that either \ref{eq:overlap1} or \ref{eq:overlap2} are false.

\eqn {
\rho(t) \equiv P(overlap_k) \leq 
P(\mu^* - \hat{\mu}^* \geq \epsilon) + P(\hat{\mu}_k - \mu_k \geq \epsilon)  \;\;\;\text{ if } \epsilon \leq a/4
}

Now for random variables $W_{sij} = P(Y|X_i=j)$ drawn from a Bernoulli distribution with mean $p_{ij}$ the Chernoff inequality gives:

\eqn {
& P(\frac{1}{t}\sum_s W_{sij} - p_{ij} \geq \gamma) \leq \exp(-\frac{t\gamma^2}{2p_{ij}(1-p_{ij})+2\gamma/3}) \\
\implies & P(\frac{1}{t}\sum_s \frac{W_{sij}}{p} - \frac{p_{ij}}{p} \geq \epsilon) = P(\hat{\mu}_i - \mu_i \geq \epsilon) \leq \exp(-\frac{tp\epsilon^2}{2+2\epsilon/3}) = \exp(-\frac{t\epsilon^2}{4+4\epsilon/3})
}
Where $p_{ij} = P(Y = 1, X_i = j) \leq P(X_i=j) = p = 1/2 \;\;\; \forall(i,j)$

Similarly

\eqn {
P(\mu^* - \hat{\mu}^* \geq \epsilon) \leq exp(-tp^2\epsilon^2) = exp(-\frac{t\epsilon^2}{4})
}

Now the estimators and their bounds are independent, as they are composed from sums of independent variables $X_i$ so the probability that $\alpha$ of them have overlapping bounds is given by a binomial distribution.

\eqn {
P(O > \alpha)  = & P(n \geq t) = 1 - \sum_{i=1}^\alpha \binom{K-1}{i}\rho(t)^{i}(1-\rho(t))^{K-1-i} \\
\leq & \exp(-(K-1)D(\frac{\alpha}{K-1} || \rho(t))
}

\eqn {
E[n] = \sum_{t=1}^\infty P(n \geq t) \leq & \sum_{t=1}^\infty \left( \exp(-\frac{t\epsilon^2}{4+4\epsilon/3}) +exp(-\frac{t\epsilon^2}{4}) \right) \\
= & \frac{1}{\exp(\epsilon^2/(4+4\epsilon/3)) - 1} + \frac{1}{\exp(\epsilon^2/4) - 1} \\
\leq & \frac{2}{\exp(\epsilon^2/(4+4\epsilon/3)) - 1} \\
= & \frac{2}{\exp(a^2/(64+4a/3)) - 1}
}

So the regret for the observe stage is bounded by:

\eqn {
R \leq \frac{2a}{\exp(a^2/(64+4a/3)) - 1}
}
